Verifying Demonstrations

### 2018-05-30 paper/RelatedWork.tex
le monde references

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility. 
Finally, DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
\seb{mention the method used by Le Monde}

>>>>

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.

Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability of privacy guarantees.
